Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-17 Ben_Manuscripts/transport/Draft.tex
Edits to draft

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement the $z$-direction.
  % BJC: could add more detail about which algorithm and cost function
  % penalty I used. Seems unnecessary since it is all in my code.

  \subsection{Identification of Hydrogen Bonds}\label{method:hbonds}

@@

@@

@@

  We found that the distributions best fit a power law / exponential
  distribution.
  % BJC: need to do this. 
  % BJC: reporting median doesn't work great since it is usually equal
  % to the lowest possible value since time step is large.
  % Would probably be better to report fit parameters (alpha for power law)
  % Could use those values in analytical equations for median

@@

  Before beginning the analysis of transport behavior, it is important to
  elucidate the topology of the membrane pores in solvated systems.

  In contrast to our previous work with a dry version of this 
  membrane, the pore region of the 5 and 10 wt\% water 
  systems are primarily filled with water and sodium ions. We define the
  pore region based on the average COM position of the monomer head groups' 
  % BJC: not sure the best place in paper to define pore region. Maybe a system definitions section in Methods.
  % BJC: need to decide on exact definition. Should probably be the same as the 'Head Groups' line
  carboxylate oxygen atoms. Figure~\ref{fig:component_densities} plots the RDF of each membrane
  constituent in the dry system as well as the 5 and 10 wt\% water systems. 
  In dry systems, the pore center is densely filled with sodium ions and head
  groups. The peak head group density occurs within 0.25 nm of the pore center.
  In hydrated systems, water occupies, and is densest, at the center of each 
  pore. The density of sodium ions is somewhat uniform in the pore center of
  the 5 wt\% water system while it shows a maximum closer to the head groups
  in the 10 wt\% water system. The peak density of sodium ions is not at the
  pore center in the 10 wt\% water system likely because they are still
  loosely associated with the monomer's carboxylate head groups.

  Pores in the 10 wt\% water system are wider and less crowded by monomers than
  those in the 5 wt\% water system. The peak head group density of 10 wt\% water
  systems is about 0.2 nm further from the pore center than the 5 wt\% water system. 
  Based on these observations, we expect solute transport to be fastest in the 10 wt
 \% water system.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_dry.pdf}
  %BJC: simulation is extended to smooth out these curves
  \caption{Dry System}\label{fig:component_density_dry}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  %MRS2: interesting that the head group max is near the transition point where water/tail groups 
  \caption{The radial densities of various monomer components paint a 
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to 
  the color-coded monomer pictured in the upper right corner of the figure. 
  All RDFs represent the number of atoms located at a given distance from the
  pore center normalized by the volume of the annular bin to which they belong.
  (a) In the dry system, the density of head groups and sodium ions are highest
  within 0.25 nm of the pore center. (b) In the 5 wt\% system, monomer head 
  groups retreat about 0.2 nm radially in order to make room for water molecules.
  (c) Monomers in the 10 wt\% system retreat an additional 0.2 nm to make room
  for more water.}\label{fig:component_densities}
  \end{figure}

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28\% and 31\% of the total water is present in the tail
  regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information for more details. This 
  result is due to a combination of the lower density of the tail region
  as well as oxygen atoms at the ends of each monomer tail which can further 
  stabilize water molecules. See Figure~\ref{S-fig:total_density} of the 
  Supporting Information for a graphical illustration of this point.

@@

  We observed transport of sodium, water and 20 other small polar solutes
  inside the membrane nanopores. First, we will comment on transport of the
  membrane constituents, water and sodium, in a system absent of any additional
  solutes. Then we will present the general trends that we observe among the
  set of solutes studied.

@@

  In the 10 wt\% water system, water molecules that spend the majority of 
  their time in the distal tail region move significantly slower than those
  confined to the pore region. In Figure~\ref{fig:water_msd_comparison}, we 
  constructed the MSD curves based on water molecules that spent > 95\% of their
  time in the pore region. If we instead restrict our calculation to water molecules
  that spend > 95\% of their time in the distal tail region, the MSD of distal tail
  water decreases 8-fold compared to pore water.

  % Changing pore radius does not change conclusion here.
  In the 5 wt\% water system, water molecules that spend the majority of their 
  time in the distal tail region have MSDs comparable to those of water molecules
  which stay in the pore region. The MSD of distal tail water molecules is 1.71 nm$^2$,
  which is actually higher than that of pore water. This anomaly is likely a consequence
  of low density in the distal tails as well as structuring of water molecules. 
  Water molecules are less likely to interact via hydrogen bonding while in the distal 
  tail region since they are interspersed between chains, while they are in close
  proximity in the pores.
  % BJC: quantify this. Number of hbonds per frame.

@@

  We observe trends in transport properties that are dependent on the chemical 
  environment within the nanopores rather than just solute size. Polar solutes
  are slowed by interactions between monomer functional groups and ions. Solutes
  with hydrophobic character partition out of the pore and are slowed by densely
  packed organic monomer components. A thorough understanding of these interactions
  will help us to create monomer design principles. We will begin our analysis by
  considering the collective trends observed across all systems and then focus on
  subsets of similar molecules.
%  where some exceptions occur.

%  We have gained a clearer picture of the general transport properties exhibited by
%  this system through the collective study of all solutes. We will first address the
%  questions posed in the introduction in a general sense before addressing them with
%  respect to specific molecules, where exceptions occur.
%  \bigskip

  Like water and sodium above, the MSDs of the solutes studied in this work are 
  significantly larger in the 10 wt\% system than those in the 5 wt\% water 
  system (Figure~\ref{fig:msds}). The fastest moving solute in both cases, 
  methanol, has an MSD about 175 times larger in the 10 wt\% versus the 5 wt 
 \% water system. Clearly the equilibrium water content of a given LLC system will 
  determine its viability for real separations.

  The MSDs are not solely a function of solute size. We plotted each solute's radius
  against their MSD in Figures~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
  Of all the solutes, we believe methanol is subject to the least hindrance by
  the membrane due its small size. Therefore we fit Equation~\ref{eqn:stokes-einstein}
  so that it intersected methanol's MSD. The uncorrected version of 
  Equation~\ref{eqn:stokes-einstein} is plotted and converges to the same value as the
  corrected form for large radii (see Section~\ref{method:stokes}). Although both curves are 
  approximations, they illustrate that the majority of solutes in our study show
  lower than expected MSDs. In most cases, the predicted MSDs even fall below the 
  conservative uncorrected Stokes-Einstein estimate. It is clear that more complex
  mechanisms determine the MSDs of these solutes.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and the hops occur when solutes are close to the pore center. (b) The
  time-averaged MSD of ethanol is sub-linear which suggests transport is governed 
  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
  \end{figure}

  The complex and non-homogeneous structure of the membrane leads to radially
  dependent transport mechanisms. In general, we observed that hops 
  made in the pore region are about 45\% larger than those made outside
  the pore region (See Figure~\ref{fig:hop_lengths}). There is a high 
  resistance to movement in the alkane-dense head group and tail regions
  while, in the pore region, solutes can move relatively freely since it 
  is primarily composed of water molecules. However, time spent in the 
  pore region does not necessarily lead to more frequent hopping. The 
  largest solutes in this study spend the most time in the pore region
  (see Figure~\ref{fig:frac_time}), but many hop with a below-average
  frequency (see Figure~\ref{fig:hopfreq}). Therefore, trapping mechanisms
  controlled by membrane properties other than density must be prevalent.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{hop_length.pdf}
  \caption{}\label{fig:hop_lengths}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{frac_time_spent.pdf}
  \caption{}\label{fig:frac_time}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hopfreq_total.pdf}
  \caption{}\label{fig:hopfreq}
  \end{subfigure}
  \caption{(a) Hops made in the pore region of the 10 wt\% water system 
  are, on average, 45\% larger than those made outside the pore region. 
  The trend in hop lengths is similar to the trend in MSDs shown in 
  Figure~\ref{fig:all_msds_10wt} implying that solutes which make consistently 
  larger hops have higher MSDs. The fraction of time spent by a solute in the 
  pore region (b) does not necessarily lead to more frequent hopping (c). For
  example, ribose spends the largest fraction of time in the pore region, yet
  performs the the second lowest number of hops.}\label{fig:hops}
  \end{figure}

  In addition to solute trapping in dense monomer regions, 
  we observe a second trapping mechanism caused by preferential hydrogen 
  bonding between hydrogen bond donor solutes and monomer head groups. To 
  continue with our ethanol example, we observe that 64\% of ethanol 
  molecules donate hydrogen bonds  % 15.7/24 donated, 0.6/24 accept -- BJC: double check these numbers
  and 3\% of ethanol molecules accept hydrogen bonds each frame. On average, 40\%
  of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
  head groups, 25\% go to the ether linkages between the tails and the 
  head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molcules in pores 
  carboxylate oxygen atoms in the pore than there are water molecules yet more
  hydrogen bonds are donated to them. The stability of hydrogen bonds with 
  carboxylate oxygen atoms is high because they have a negative charge
  with no neutralizing positive charges nearby. Additionally, on average, 
  each sodium ion is coordinated to 1.7 water molecules meaning an appreciable
  fraction of the water molecules occupying the pore region are usually 
  coordinated to a sodium ion which decreases their availability to accept 
  hydrogen bonds from solutes.
  % MRS1: this should lead to reduced ability to solvate positive things, but 
  % shouldn't reduce H-bonding that much?
  % BJC1: I think that it takes away acceptor oxygen atoms since they are occupied
  % by sodium. The hydrogen atoms of water could still hbond but I'm just talking
  % about ethanol donating to water's oxygen, for which opportunities should be suppressed.

  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
  % me maybe half a day to implement and generate results. Not sure if necessary though since
  % I'm just going to say that I don't know what distribution it is and we are going to
  % use a percentile.
  Hydrogen bond lifetimes appear to be distributed according to a power law or an
  exponential function. A number of researchers provide evidence that supports a 
  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
  studies were done on extremely short timescales relative to ours, outputting positions
  every timestep. Voloshin et al. studied hydrogen bonding on multiple timescales and 
  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
  We do not collect data frequently enough to provide a sufficient answer to this 
  question so we instead report the 95\textsuperscript{th} percentile of hydrogen bond dwell times.
  This places emphasis on solutes with long dwell times.

  The lifetime of hydrogen bonds between solutes and monomer head groups tends to 
  be longer for solutes that hydrogen bond more frequently. In Figure~\ref{fig:hbonds}
  we see nearly the same ordering of the percentage of solutes hydrogen bonded to
  monomer head groups and the mean hydrogen bond lifetime. Solutes with multiple
  hydroxyl groups donate hydrogen bonds most frequently and tend to stay hydrogen
  bonded longer. Hydrogen bonds donated by nitrogen are far less common and tend 
  to be short-lived as supported by acetamide and urea.

@@

  Finally, we observe slowing or immobilization of solutes that associate with
  sodium counterions. Much like water, the polarity of the solutes creates 
  regions of high electron density, modeled using partial negative charges, 
  which are stabilized through electrostatic interactions with sodium ions. 
  In Figure~\ref{fig:na_coordination}, we've plotted the percentage
  of sodium ions coordinated to the oxygen atoms of each solute as well as the
  average length of time that pairs stay coordinated. The degree and length of 
  coordination between solutes and sodium in the 5 wt\% water system is higher
  in all cases than that in the 10 wt\% water systems. The crowded pores of 
  the 5 wt\% water system forces sodium ions in close proximity to solutes. 
  The 5 highest coordinated solutes, which also have the longest coordinated dwell times,
  all contain carbonyl groups (except for dimethyl sulfoxide which has an 
  analogous sulfinyl group) which leaves a highly electron-dense oxygen atom 
  exposed and ready to interact with sodium. 
  %BJC: need to verify following  
  The dwell times are power law 
  distributed, which means that while many of these interactions are fleeting,
  there is still a chance for very long periods of association to occur. For 
  example, the longest period of coordination between acetone and sodium was
  110 ns.
%  There are many cases, particularly when an electronegative atom is left unprotected,
%  in which polar groups bind to sodium ions for at least a short period of time.

  % need to think a little more about this. Numbers get skewed by different numbers
  % of oxygen atoms per solute. For example, the carbonyl group of acetic acid
  % associates with sodium a lot, but the OH doesn't really. (28 % C=O versus 3 % COH)
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_solutes_NA_coordination.pdf}
  \caption{}\label{fig:all_solutes_NA_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_NA_dwells.pdf}
  \caption{}\label{fig:all_NA_dwells}
  \end{subfigure}
  \caption{(a) Solutes, especially those with carbonyl groups, spend a 
  significant fraction of time coordinated to sodium ions. (b) The length
  of time a solute-sodium pairs spends associated tends to be higher for
  pairs that associate more frequently.}\label{fig:na_coordination}
  \end{figure}

  Coordination of ions with oxygen has been observed in a variety of systems. 
  Carvajal et al. noted that Na\textsuperscript{+} coordinated with four 
  tetrahydrofuran molecules when they dissolved a sodium salt in the solvent.~\cite{carvajal_studies_1965}
  Wu et al. observed coordination of Na\textsuperscript{+} with the carbonyl
  group of a molecule used to design an organic electrode.~\cite{wu_unraveling_2015} 
  Finally, Shinoda et al. observed K\textsuperscript{+} ions coordinated with
  the carbonyl and hydroxyl groups of carboxy-terminal groups in crystallized
  ATPase.~\cite{shinoda_crystal_2009}

>>>>

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement the $z$-direction.
  We reported the standard error in the average hop lengths by 
  bootstrapping the hop lengths.
  % BJC: could add more detail about which algorithm and cost function
  % penalty I used. Seems unnecessary since it is all in my code.

  % This might change
  We determined the frequency of hops by dividing the total number of 
  hops by the total length of the simulation. We used the normal 
  approximation in order to estimate the 95 \% confidence interval
  of these estimates:
  \begin{equation}
  95\%~CI = 1.96 \sqrt{\dfrac{\lambda}{n}}
  \end{equation}
  where $\lambda$ is the average frequency of hops and n is the total
  observation time accumulated for all solutes.

  Where instructive, we differentiated between the length of hops inside
  and outside of the pores. For 10 wt\% water systems, we consider a solute
  to be in the pore if it is within 0.75 nm of a pore center. This radial
  cut-off maximizes the difference between average hop lengths in and out
  of the pore. See Section~\ref{S-section:pore-region} of the Supporting
  Information for further details on this optimization.

  \subsection{Time Spent in Pore Region}

  Using the cut-off defined above, we calculated the fraction of time
  that a solute spends within the pore region. Since this is a process
  with two possible outcomes, we calculated the standard error ($SE$) of our
  calculations based on the binomial theorem: 
  \begin{equation}
  SE = \sqrt{\dfrac{p(1-p)}{n}}
  \end{equation}
  where $p$ is the probability that a solute is in the pore region and
  $n$ is the sample size. Here $n$ is the total number of transitions
  between each region.

  \subsection{Identification and Analysis of Hydrogen Bonds}\label{method:hbonds}  % Could just make title 'Hydrogen Bonds'

@@

  We determined the average percentage of solutes which actively participated
  in a hydrogen bond interaction with monomers each frame. We only counted
  unique solute--monomer hydrogen bond interactions meaning solutes
  that hydrogen bond more than once simultaneously were classified as a
  single pairing event. We determined the standard error of this calculation
  by bootstrapping over each solute's trajectory. For each bootstrap trial,
  we randomly chose 24 solutes with replacement and calculated the average
  active solute-monomer hydrogen bonds per frame.

@@

  We determined the average percentage of solutes actively coordinated to
  a sodium ion each frame. Our calculation procedure is analogous to that for
  solute-monomer hydrogen bond interactions outlined in the previous section.

@@

  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
  % me maybe half a day to implement and generate results. Not sure if necessary though since
  % I'm just going to say that I don't know what distribution it is and we are going to
  % use a percentile.
  Hydrogen bond lifetimes appear to be distributed according to a power law or an
  exponential function. A number of researchers provide evidence that supports a 
  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
  studies were done on extremely short timescales relative to ours, outputting positions
  every time step. Voloshin et al. studied hydrogen bonding on multiple timescales and 
  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
  Due to memory limitations, we could not collect data frequently enough to provide a
  sufficient answer to this question so we instead report the 95\textsuperscript{th} 
  percentile of hydrogen bond dwell times. This places emphasis on solutes with 
  long dwell times. We reported the standard error of this calculation by bootstrapping
  the distribution of dwell times.

  The distribution of sodium association lifetimes appear similar to
  hydrogen bond life time distributions. Therefore, we reported association
  lifetimes in the same manner as hydrogen bond lifetimes.

@@

  Before beginning the analysis of solute transport behavior, it is important to
  elucidate the topology of the membrane pores in solvated systems.

  In contrast to our previous work with a dry version of this membrane, the 
  region close to the pore center of the 5 and 10 wt\% water systems is 
  primarily filled with water and sodium ions. Figure~\ref{fig:component_densities}
  plots the RDF of each membrane constituent in the dry system as well as the
  5 and 10 wt\% water systems. In dry systems, the pore center is densely 
  filled with sodium ions and head groups. The peak head group density occurs
  within 0.25 nm of the pore center. In hydrated systems, water occupies, 
  and is densest, at the center of each pore. The density of sodium ions is 
  somewhat uniform in the pore center of the 5 wt\% water system while it shows
  a maximum closer to the head groups in the 10 wt\% water system. The peak 
  density of sodium ions is not at the pore center in the 10 wt\% water system
  likely because they are still loosely associated with the monomer's carboxylate
  head groups.

  Pores in the 10 wt\% water system are wider and less crowded by monomers than
  those in the 5 wt\% water system. The peak head group density of 10 wt\% water
  systems is about 0.2 nm further from the pore center than the 5 wt\% water system. 
  Based on these observations, we expect solute transport to be fastest in the 
  10 wt\% water system.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_dry.pdf}  % running this out on bridges to make smoother
  %BJC: simulation is extended to smooth out these curves
  \caption{Dry System}\label{fig:component_density_dry}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  %MRS2: interesting that the head group max is near the transition point where water/tail groups 
  \caption{The radial densities of various monomer components paint a 
  picture of the pore topology where the pore centers of hydrated systems are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to 
  the color-coded monomer pictured in the upper right corner of the figure. 
  All RDFs represent the number of atoms located at a given distance from the
  pore center normalized by the volume of the annular bin to which they belong.
  (a) In the dry system, the density of head groups and sodium ions are highest
  within 0.25 nm of the pore center. (b) In the 5 wt\% system, monomer head 
  groups retreat about 0.2 nm radially in order to make room for water molecules.
  (c) Monomers in the 10 wt\% system retreat an additional 0.2 nm to make room
  for more water.}\label{fig:component_densities}
  \end{figure}

  There is an appreciable amount of water that partitions into the distal tail % BJC: defined in methods
  region of both systems. 28\% and 31\% of the total water is present in the
  tail regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information 
  for more details on the equilibration that led to this conclusion. The partition
  is due to a combination of the distal tail region's lower density as well
  as oxygen atoms at the ends of each monomer tail which can further stabilize
  water molecules. See Figure~\ref{S-fig:total_density} of the Supporting 
  Information for a graphical illustration of this point.

@@

  We observed transport of sodium, water and 20 other small polar solutes
  inside the membrane nanopores. First, we will comment on transport of the
  membrane constituents, water and sodium, in a system absent of any additional
  solutes. Then we will present the general trends that we observe among the
  all other solutes studied.

@@

  In the 10 wt\% water system, water molecules that spend the majority of 
  their time in the distal tail region move significantly slower than those
  close to the pore center. In Figure~\ref{fig:water_msd_comparison}, we 
  constructed the MSD curves based on water molecules that spent $>$ 95\% of their
  time outside the distal tail region. If we instead restrict our calculation to
  water molecules that spend $>$ 95\% of their time in the distal tail region, 
  the MSD of distal tail water decreases 8-fold.

  % Changing pore radius does not change conclusion here.
  In the 5 wt\% water system, water molecules that spend the majority of their 
  time in the distal tail region have MSDs comparable to those of water molecules
  close to the pore center. The MSD of distal tail water molecules is 1.71 nm$^2$.
  This anomaly is likely a consequence of low density in the distal tails (see
  Figure~\ref{S-fig:total_density}) as well as structuring of water molecules via
  hydrogen bonding. Water molecules are less likely to hydrogen bond while in the
  distal tail region since they are interspersed between chains, while those in 
  the pores stay in close proximity to each other. We observed about 9 times more  % tailvpore_hbonding.py in figures folder
  hydrogen bonding between water molecules near the pore center versus those in 
  the distal tail region. While a similar observation holds for the 10 wt\% system,
  its high water content facilitates a less crowded environment where diffusion
  of water molecules dominates.

@@

  We observe trends in transport properties that are dependent on the chemical 
  environment within the nanopores rather than just solute size. Polar solutes
  are slowed by interactions between monomer functional groups and ions. Solutes
  with hydrophobic character partition out of the pore and are slowed by densely
  packed organic monomer components. A thorough understanding of these interactions
  will help us to create monomer design principles. We will begin our analysis by
  considering the collective trends observed across all systems and then focus on
  subsets of similar molecules.

  Like water and sodium above, the MSDs of the solutes studied in this work are 
  significantly larger in the 10 wt\% system than those in the 5 wt\% water 
  system (Figure~\ref{fig:msds}). The fastest moving solute in both cases, 
  methanol, has an MSD about 175 times larger in the 10 versus the 5 wt\%
  water system. Clearly the equilibrium water content of a given LLC system will 
  determine its viability for real separations.  % BJC: last sentence too much speculation?

  The MSDs are not solely a function of solute size. We plotted each solute's radius
  against their MSD in Figures~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
  Of all the solutes, we believe methanol is subject to the least hindrance by
  the membrane due its small size. Therefore we fit Equation~\ref{eqn:stokes-einstein}
  so that it intersected methanol's MSD. The uncorrected version of 
  Equation~\ref{eqn:stokes-einstein} ($f$=1) is plotted and converges to the same value as the
  corrected form for large radii (see Section~\ref{method:stokes}). Although both curves are 
  approximations, they illustrate that the majority of solutes in our study show
  lower than expected MSDs. In most cases, the predicted MSDs even fall below the 
  conservative uncorrected Stokes-Einstein estimate. It is clear that more complex
  mechanisms determine the MSDs of these solutes.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and more frequent hops occur when solutes are close to the pore center.
  (b) The time-averaged MSD of ethanol is sub-linear which suggests transport is
  governed by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
  \end{figure}

  The complex and non-homogeneous structure of the membrane leads to radially
  dependent transport mechanisms. In general, we observed that hops 
  made in the pore region are about 59\% larger than those made outside
  the pore region (see Figure~\ref{fig:hop_lengths}). There is a high 
  resistance to movement in the alkane-dense head group and tail regions
  while, in the pore region, solutes can move relatively freely since it 
  is primarily composed of water molecules. However, time spent in the 
  pore region does not necessarily lead to more frequent hopping. The 
  largest solutes in this study spend the most time in the pore region
  (see Figure~\ref{fig:frac_time}), but many hop with a below-average
  frequency (see Figure~\ref{fig:hopfreq}). Therefore, trapping mechanisms
  controlled by membrane properties other than alkane density must be prevalent.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{hop_length.pdf}
  \caption{}\label{fig:hop_lengths}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{frac_time_spent.pdf}
  \caption{}\label{fig:frac_time}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{hopfreq_total.pdf}
  \caption{}\label{fig:hopfreq}
  \end{subfigure}
  \caption{(a) Hops made in the pore region of the 10 wt\% water system 
  are, on average, 59\% larger than those made outside the pore region. 
  The trend in hop lengths is similar to the trend in MSDs shown in 
  Figure~\ref{fig:all_msds_10wt} implying that solutes which make consistently 
  larger hops have higher MSDs. The fraction of time spent by a solute in the 
  pore region (b) does not necessarily lead to more frequent hopping (c). For
  example, ribose spends the largest fraction of time in the pore region, yet
  hops the fifth least frequently.}\label{fig:hops}
  \end{figure}

  %In addition to solute trapping in dense monomer regions, 
  We observe a second trapping mechanism caused by preferential hydrogen 
  bonding between hydrogen bond donor solutes and monomer head groups. To 
  continue with our ethanol example, we observe that 64\% of ethanol 
  molecules donate hydrogen bonds  % 15.7/24 donated, 0.6/24 accept -- BJC: double check these numbers
  and 3\% of ethanol molecules accept hydrogen bonds each frame. On average, 40\%
  of hydrogen bonds donated by ethanol go to carboxylate % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
  head groups, 25\% go to the ether linkages connecting the monomers tails to the 
  head groups and the remaining 35\% to water. There are about 46\% less  % 800 carboxylate oxygens total versus 2158 * 0.69 total water molcules in pores 
  carboxylate oxygen atoms in the pore than there are water molecules yet more
  hydrogen bonds are donated to them. The stability of hydrogen bonds with 
  carboxylate oxygen atoms is high because they have a negative charge
  with no neutralizing positive charges nearby. Additionally, on average, 
  each sodium ion is coordinated to 1.7 water molecules meaning an appreciable
  fraction of the water molecules occupying the pore region are usually 
  coordinated to a sodium ion which decreases their availability to accept 
  hydrogen bonds from solutes.
  % MRS1: this should lead to reduced ability to solvate positive things, but 
  % shouldn't reduce H-bonding that much?
  % BJC1: I think that it takes away acceptor oxygen atoms since they are occupied
  % by sodium. The hydrogen atoms of water could still hbond but I'm just talking
  % about ethanol donating to water's oxygen, for which opportunities should be suppressed.

  The lifetime of hydrogen bonds between solutes and monomer head groups tends to 
  be longer for solutes that hydrogen bond more frequently. In Figure~\ref{fig:hbonds}
  we see nearly the same ordering of the percentage of solutes hydrogen bonded to
  monomer head groups and the 95\textsuperscript{th} percentile of hydrogen bond 
  lifetimes. Solutes with multiple hydroxyl groups donate hydrogen bonds most 
  frequently and tend to stay hydrogen bonded longer. Hydrogen bonds donated by
  nitrogen are far less common and tend to be short-lived as shown by acetamide
  and urea.

@@

  Finally, we observe slowing or immobilization of solutes that associate with
  sodium counterions. Much like water, the polarity of the solutes creates 
  regions of high electron density, modeled using partial negative charges, 
  which are stabilized through electrostatic interactions with sodium ions. 
  In Figure~\ref{fig:na_coordination}, we've plotted the percentage
  of sodium ions coordinated to the oxygen atoms of each solute as well as the
  95\textsuperscript{th} percentile of sodium association times. The degree and length of 
  coordination between solutes and sodium in the 5 wt\% water system is higher
  in all cases than that in the 10 wt\% water systems. The crowded pores of 
  the 5 wt\% water system forces sodium ions in close proximity to solutes.

  Carbonyl functional groups tend to associate with sodium the most. Nearly
  all of the most coordinated solutes contain a carbonyl group (except for 
  DMSO which has an analogous sulfinyl group). There is a significant
  drop in sodium ion association for solutes that do not contain carbonyl 
  groups or multiple hydroxyl groups to compensate. The corresponding dwell
  times follow a similar trend, however the dwell times of highly coordinated 
  solutes with multiple hydroxyl groups are generally lower since association
  between hydroxyl groups and sodium is apparently a weaker interaction. Carbonyl
  groups contain an exposed and highly electron-dense oxygen atom which interacts
  readily with sodium ions. Carbonyl groups with nitrogen substituents appear
  to interact with sodium more frequently than those with carbon substituents. 
  Acetone associates with sodium significantly less than urea and acetamide.

%  The dwell times are power law 
%  distributed, which means that while many of these interactions are fleeting,
%  there is still a chance for very long periods of association to occur. For 
%  example, the longest period of coordination between acetone and sodium was
%  110 ns.
%  There are many cases, particularly when an electronegative atom is left unprotected,
%  in which polar groups bind to sodium ions for at least a short period of time.

  % need to think a little more about this. Numbers get skewed by different numbers
  % of oxygen atoms per solute. For example, the carbonyl group of acetic acid
  % associates with sodium a lot, but the OH doesn't really. (28 % C=O versus 3 % COH)
  \begin{figure}[!htb]
  \centering
  % BJC: maybe I should normalize these to number of oxygen atoms?
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_solutes_NA_coordination.pdf}  % all_coord.py
  \caption{}\label{fig:all_solutes_NA_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_NA_dwells.pdf}  % na_dwells.py
  \caption{}\label{fig:all_NA_dwells}
  \end{subfigure}
  \caption{(a) Solutes, especially those with carbonyl groups, spend a 
  significant fraction of time coordinated to sodium ions. (b) The length
  of time a solute-sodium pairs spends associated tends to be higher for
  pairs that associate more frequently.}\label{fig:na_coordination}
  \end{figure}

  Coordination of ions with oxygen has been observed in a variety of systems. 
  Carvajal et al. noted that Na\textsuperscript{+} coordinated with four 
  THF molecules when they dissolved a sodium salt in the solvent.~\cite{carvajal_studies_1965}
  Wu et al. observed coordination of Na\textsuperscript{+} with the carbonyl
  group of a molecule used to design an organic electrode.~\cite{wu_unraveling_2015} 
  Finally, Shinoda et al. observed K\textsuperscript{+} ions coordinated with
  the carbonyl and hydroxyl groups of carboxy-terminal groups in crystallized
  ATPase.~\cite{shinoda_crystal_2009}
